---
title: "Word Cloud"
author: "Liwen Huang"
date: "8/25/2018"
output: rmarkdown::github_document
---

Import some library
```{r, results='hide',fig.keep='all'}
library(dplyr)
```

You want to build a word cloud, an infographic where the size of a word corresponds to how often it appears in the body of text.
To do this, you'll need data. Write code that takes a long string and builds its word cloud data in a dictionary ↴ , where the keys are words and the values are the number of times the words occurred.

Think about capitalized words. For example, look at these sentences:
```{r}
sentence1="After beating the eggs, Dana read the next step:"
sentence2="Add milk and eggs, then add flour and sugar."
```

First of all, I have written a function that counts words. This function returns a matrix with two columns, the first one indicate the word, the second the number of times it appears in the sentence
```{r}
countword<-function(sentence){
 word_count=sentence%>%
  tolower()%>%gsub('[[:punct:] ]+',' ',.)%>%
  noquote()%>%strsplit(split=' ')%>%unlist%>%
  table()%>%as.matrix()
 return (word_count)
}
```

test the function
```{r}
t1=countword(sentence1)
t2=countword(sentence2)
t1
t2
```

Then use a function to aggregate the total word counts
```{r}
total_wordcount<-function(count1, count2){
  total=rbind(count1, count2)
  total=data.frame(rownames(total), total)
  aggregate(. ~ rownames.total., data=total, FUN=sum)  
}
```

test the function
```{r}
t3=total_wordcount(t1, t2)
t3
```

Now I can make my little word cloud
```{r}
library(wordcloud)
library(RColorBrewer)

t3_cloud=wordcloud(words=t3$rownames.total., freq=t3$total, min.freq = 1,
         max.words=200, random.order=FALSE, rot.per=0, 
         colors=brewer.pal(8, "Dark2"))
```

